Enhancement of SDR in Thessaloniki

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 19:12
Commit 2024-09-06 23:11

\caption{ - empty caption - }\label{fig:unnamed-chunk-7}
\end{figure}

@@

@@

\begin{verbatim}
2024-09-06 10:32:08.3 athan@sagan GHI_enh_08_validation.R 1.913171 mins
\end{verbatim}

>>>>

\caption{ - empty caption - }\label{fig:unnamed-chunk-7-1}
\end{figure}

@@

\begin{verbatim}
Loading required package: ggpp
\end{verbatim}

\begin{verbatim}
Registered S3 methods overwritten by 'ggpp':
  method                  from   
  heightDetails.titleGrob ggplot2
  widthDetails.titleGrob  ggplot2
\end{verbatim}

\begin{verbatim}
Attaching package: 'ggpp'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:ggplot2':

    annotate
\end{verbatim}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-2}

\caption{ - empty caption - }\label{fig:unnamed-chunk-7-2}
\end{figure}

@@

\begin{verbatim}
2024-09-06 19:52:22.8 athan@tyler GHI_enh_08_validation.R 21.715553 mins
\end{verbatim}
